Efficient pedigree recording for fast population genetics simulation

### 2017-12-27 forwards_paper.tex
add comment
add into para to run time section

@@

\plr{Refer to simulation results here.}

>>>>

\krt{Empirically, I did find that simplifying more often than every 1,000 generations gave a run-time hit of about 25
percent???}

@@

The simulation results shown in Figures \ref{fig:runtimes_selection} and \ref{fig:relative_speedup_selection} show that
pedigree tracking greatly speeds up forward-time simulations.  Further, the run times with pedigree tracking become
near-linear in $rho$ (Figure \ref{fig:runtimes_selection}).  In this section, we explore the run-time complexity using a
simplified Wright-Fisher model with recombination.
